NLO QCD+EW corrections to diphoton production in association with a vector boson

### 2017-10-30 conclusions.tex
minor updates in text

We calculated the next-to-leading order QCD and electroweak corrections to these three processes for a set
of realistic fiducial cuts. Particular
emphasis has been put on the up to now unknown electroweak corrections as well as the combination of QCD and
electroweak corrections with the aim of producing the most precise prediction possible within the Standard Model.
As expected, we found the QCD corrections to be large and dominant compared to the electroweak corrections when 
calculating the corrections to the total cross sections. QCD corrections are particular large for these processes due to new
channels opening up at NLO but can effectively be reduced by applying a jet veto. Electroweak corrections
lead to moderate corrections to the total cross section of up to $4.4\%$ for the $\gamma\gamma \ell^{+}\ell^{-}$ 
process. However, in the high energy tail of differential distributions the electroweak corrections become increasingly important
and can lead to corrections of up to $30 \%$. Electroweak corrections become important in the same regions where one
also expects increasing effects of higher dimensional operators. The precise determination of limits on higher dimensional 
operators therefore requires the inclusion of higher order correction of both QCD as well as of the electroweak interaction.

>>>>

We calculated the next-to-leading order QCD and electroweak corrections to these three processes for a set
of realistic fiducial cuts. Particular
emphasis has been put on the up to now unknown electroweak corrections as well as the combination of QCD and
electroweak corrections with the aim of producing the most precise prediction possible within the Standard Model.
As expected, we found the QCD corrections to be large and dominant compared to the electroweak corrections when 
calculating the corrections to the total cross sections. QCD corrections are particular large for these processes due to new
channels opening up at NLO but can effectively be reduced by applying a jet veto. Electroweak corrections
lead to moderate corrections to the total cross section of up to $4.4\%$ for the $\gamma\gamma \ell^{+}\ell^{-}$ 
process. However, in the high energy tail of differential distributions the electroweak corrections become increasingly important
and can lead to corrections of up to $30 \%$. Electroweak corrections become important in the same regions where one
also expects increasing effects of higher dimensional operators. The precise determination of limits on higher dimensional 
operators therefore requires the inclusion of higher order correction of both QCD as well as of the electroweak interaction.
We also compared the two possibilities of combining QCD with electroweak corrections, namely either in an additive or
in a multiplicative way. One expects that the difference between the two schemes is small as they can be seen as an estimation
of neglected higher order contributions. We found that although this is true on the level of total cross sections there can be 
regions in phase space where the leading order contribution vanishes and therefore the k-factor become infinitely large. 
For those kinematical edges we observe a breakdown of the multiplicative scheme whereas the additive scheme provides
a reliable estimation of the higher order uncertainties throughout the whole phase space.

### 2017-10-30 results.tex
minor updates in text

Finally, in Figure \ref{fig:aaa:dphi} we show the azimuthal 
separation $\Delta\phi$ between all three diphoton pairs. 
Similar features as before are visible as both the NLO QCD 
and NLO EW corrections relax the kinematic boundaries of 
the leading order calculation. 
Especially the azimuthal separation of the leading and 
third leading photon receives substantial shape corrections 
throughout the entire spectrum, with and without the 
presence of a jet veto. 
The electroweak corrections are negligible for this 
observable.

@@

In Figure \ref{fig:aaz:dphi} we consider the azimuthal separation 
between the leading and subleading photon, and both the leading 
and subleading photon and the lepton pair.
While both photons tend to be back-to-back, the azimuthal 
separation of the leading photon and the lepton pair exhibits 
a kinematic edge at LO, restricting it to be larger than 
$\tfrac{1}{2}\,\pi$. 
\comment{MS: Do we understand why this is?}
On the contrary, the azimuthal separation of the subleading 
photon and the lepton pair exhibits no such limit at LO and 
instead peaks at roughly $\Delta\phi=\tfrac{1}{2}\,\pi$. 
The QCD corrections, with the exception of the aforementioned 
edge, are generally flat, taking values of $\deltaQCD\approx 0.3$ 
in the absence and $\deltaQCD\approx 0.2$ in the presence 
of a jet veto. 
The electroweak corrections are equally flat and amount to 
$\deltaEW\approx-4\%$. 
Their additive and multiplicative combinations are very 
similar.

>>>>

Finally, in Figure \ref{fig:aaa:dphi} we show the azimuthal 
separation $\Delta\phi$ between all three diphoton pairs. 
Similar features as before are visible as both the NLO QCD 
and NLO EW corrections relax the kinematic boundaries of 
the leading order calculation. 
Especially the azimuthal separation of the leading and 
third leading photon receives substantial shape corrections 
throughout the entire spectrum, with and without the 
presence of a jet veto. The angular distribution between leading photon
and the second or third subleading photon exhibit a kinematical edge at $\pi/2$ which 
is relaxed at NLO. 
This kinematical edge can be understood in the following way:
 Let us consider the first observable, the angular separation between 
the leading and the subleading photon, the argument also holds for the separation between
the leading and the third leading photon. The third leading photon has to recoil against the
system of the two leading photons. Let us go into the limit where the three photons have
a very similar transverse momentum and consider the configuration where the leading
photon is back-to-back to the third leading photon. Then the second photon must 
be perpendicular to this axis. If the third photon has less transverse momentum, it 
needs the second photon to recoil against the leading photon. Therefore it gets closer
to the third photon and further away from the leading photon. $\pi/2$ is therefore the
minimal distance the second photon can have to the leading one.  Only at NLO where
one can have additional radiation this constraint is relaxed. We will see later in Fig.
\ref{fig:aaz:dphi} that this situation is also present when one replaces one of the subleading
photons by a $z$ boson. 
The electroweak corrections are negligible for this 
observable.

@@

In Figure \ref{fig:aaz:dphi} we consider the azimuthal separation 
between the leading and subleading photon, and both the leading 
and subleading photon and the lepton pair.
While both photons tend to be back-to-back, the azimuthal 
separation of the leading photon and the lepton pair exhibits 
a kinematic edge at LO, restricting it to be larger than 
$\tfrac{1}{2}\,\pi$. 
As discussed above this kinematic edge is also present in the case of the triple photon process
(see Fig. \ref{fig:aaa:dphi_}) when considering the azimuthal angle between
the leading and any subleading photon.
On the contrary, the azimuthal separation of the subleading 
photon and the lepton pair exhibits no such limit at LO and 
instead peaks at roughly $\Delta\phi=\tfrac{1}{2}\,\pi$. 
The QCD corrections, with the exception of the aforementioned 
edge, are generally flat, taking values of $\deltaQCD\approx 0.3$ 
in the absence and $\deltaQCD\approx 0.2$ in the presence 
of a jet veto. 
The electroweak corrections are equally flat and amount to 
$\deltaEW\approx-4\%$. 
Their additive and multiplicative combinations are very 
similar.
